### 2020-03-08 appendix.tex
edits

>>>>

\subsection*{A gamma approximation to generation-interval distributions}

Assuming that the intrinsic generation-interval distribution for each class (asymptomatic and symptomatic) follows a gamma distribution with mean $\bar G_c$ and dispersion $\kappa_c$, the average discount of a new infection can be written as:
\begin{equation}
\delta_c = (1 + \kappa_c r \bar G_c)^{-1/\kappa_c},
\end{equation}
which shows that the average discount increases with smaller $\bar G_c$ and with larger $\kappa_c$.
Then, the odds of the realized proportion of asymptomatic transmission can be written as:
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right],
\end{equation}
where $\bar G_a$ and $\bar G_s$ are the mean generation intervals for asymptomatic and symptomatic cases, and $\kappa_a$ and $\kappa_s$ are the generation-interval dispersions for asymptomatic and symptomatic cases.
Finally, the basic reproduction number is calculated by
\begin{equation}
\mathcal R_0 = \left(z (1 + \kappa_a r \bar G_a)^{-1/\kappa_a} + (1-z) (1 + \kappa_s r \bar G_s)^{-1/\kappa_s}\right)^{-1}.
\end{equation}
